Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-01-29 src/tex/ms.tex
address comment #1

>>>>

\rev{\subsubsection{The UV~Threshold Hypothesis as a narrow step function}
A key aspect of the UV Threshold Hypothesis is the proposed step-function dependence of abiogenesis likelihood on UV flux.
This approach stems from the constraints governing photochemical pathways, which exhibit a threshold behavior: below a certain flux, competing thermal reactions dominate, preventing abiogenesis, while above the threshold, UV photochemistry proceeds at sufficient rates, and other stochastic processes become rate-limiting.

\citet{Ranjan2017b} speculated that UV photochemistry might be rate-limiting for abiogenesis, particularly on planets orbiting M dwarfs, due to their lower baseline UV fluxes.
This could delay abiogenesis by orders of magnitude, resulting in a continuous dependence of abiogenesis likelihood on UV flux.
However, recent studies challenge this view for the cyanosulfidic scenario.
\citet{Rimmer2021}  calculated photochemical timescales on early Earth at 180-300 hours (7.5-12.5 days), significantly shorter than the ~1000-year timescale for stochastic geological events~\citep{Rimmer2023}.
Even with 1000x slower photochemistry on M-dwarf planets, abiogenesis would occur within 20-30 years — geologically negligible compared to stochastic processes — supporting the step-function model.

Nonetheless, alternative abiogenesis pathways or combinations of pathways may exhibit continuous or mixed dependencies on UV flux.
While the step-function formalism is justified for the cyanosulfidic scenario, future work should explore UV dependencies across other scenarios to refine predictions for biosignature distributions and testable hypotheses.
}
